---
title: "Rmarkdown_template 1"
author: "Jiawei Fu"
date: "1/26/2020"
output: pdf_document
---

# Basics 1

Use "#" to write the header; and you can control the size by adding more "#".

For example, in the assignment, you can:

## Question 1: here, you basically copy and paste the question.
### (a): balabala
## Solution: answer the questions here. 
### (b): balabala


You can put the codes in the R code chunk:

```{r}


```




```{r}
### r codes example
set.seed(320)

rand <- rnorm(50)   ### draw samples 
plot(density(rand))   ### plot the density 
```

Sometimes, you would like use Inline R code. You can evaluate R expressions inline by enclosing the expression within a single back-tick qualified with ‘r’.

For example, I want to know 941+134=`r 941+134`. (See rmd file how I calculate)


Creat list using the dash:

- item 1
- item 2

Emphasize with asterisk mark:

*important* or **important**


# Mathematics 1

$$

$$



Write equations between \$\$ and \$\$. For example,
$$
x_i + z^j = 8-t 
$$

You can write inline equations between two dollar signs, \$ equations \$. For example: $y_i=5x_i+6$.

Also, use COMMAND aligned and \&, one can write clean and beautiful equations: (see rmd file)
$$
\begin{aligned}
x_{ij} &+ z^{ij} = 8-t  \\
y_i+z_i+t &= \frac{5}{7}
\end{aligned}
$$

If you like the Greek letters:

$\alpha$ 
$\beta$
$\gamma$ 
$\delta$
$\theta$

